Evaluating isolation and contact tracing to control pandemic potential influenza outbreaks

### 2025-05-13 inst/paper/main.tex
add presymptomatic results

@@

>>>>

The proportion of transmission that occurs before on the onset of symptoms has a moderate affect on epidemic containment for across isolation response rates (Figure \ref{fig:prop-outbreak-control-prop-presym-iso}). In all scenarios decreasing the proportion of presympatomatic transmission result in an greater or equal probability of outbreak control. When presymptomatic transmission is minimal, most $R = 1.1$ outbreaks go extinct without any contact tracing, at any rate of isolation after symptom onset, with extinction ensured if isolated after LFT testing (Figure \ref{fig:prop-outbreak-control-prop-presym-iso} leftmost column). Furthermore, when  $<1\%$ of transmission is presymptomatic, rapidly isolating after symptoms (e.g. after self-testing) can contain more than half of outbreaks for all transmissibility scenarios ($R \leq 3.5$) (Figure \ref{fig:prop-outbreak-control-prop-presym-iso}). Conversely, when 30\% of transmission is presymptomatic, less than half of highly transmissible epidemics are controlled, even with the most optimistic isolation response time and contact tracing coverage (Figure \ref{fig:prop-outbreak-control-prop-presym-iso} rightmost column). \\

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{../plots/prop_outbreak_control_prop_presym_iso.png}
\caption{Stub.}
\label{fig:prop-outbreak-control-prop-presym-iso}
\end{figure}
